Meta-analysis

### 2020-07-08 04_MetaAnalysis.Rmd
reordering forest plot, Its a mess right now don't look

```{r Metafor-analysis}
PM_mv <- rma.mv(
   yi = grain_MD,
   vi,
   mods = ~ spray_management - 1,
   method = "ML",
   random = ~ spray_management | trial,
   struct = "UN",
   data = dat1
)
summary(PM_mv)
```

@@

Lets look at the trial variability in this model with a forest plot
```{r forestP, fig.height= 40, fig.width=10}
# If anyone knows how to fix the margins here it would be helpful!!!!!!!!!!!!!!!!
metafor::forest(PM_mv, cex =0.75 , width = 5,
                ilab = cbind(dat1$trial_ref, dat1$location, dat1$year, dat1$row_spacing, dat1$host_genotype, dat1$dose,
                             as.character(dat1$spray_management)),
                ilab.xpos = c(-6.5, -5.5,-4.75,-4.15,-3.4,-2.5,-1),
                slab = NA, 
                xlim = c(-7, 3.5),
                ylim = c(4,119),
                xlab = "Grain yield mean difference")

@@

### add column headings to the plot
text(c(-6.5, -5.5,-4.75,-4.15,-3.4,-2.5,-1), 117.9,cex = 0.85, 
     c("Trial\nReference", "Location", "Year", "Row\nSpacing","Host\nCultivar","DMI dose","SM"),
     font = 2)

>>>>

```{r Metafor-analysis}
PM_mv <- rma.mv(
   yi = grain_MD,
   vi,
   mods = ~ spray_management - 1,
   method = "ML",
   random = ~ spray_management | trial,
   struct = "UN",
   data = dat1
)
summary(PM_mv)
```
```{r}
(PM_mv$b - PM_mv$ci.ub) / PM_mv$se
```

@@

Lets look at the trial variability in this model with a forest plot
```{r forestP, fig.height= 40, fig.width=20}
change_labels <- function(x1) {
   x1 <- gsub(pattern = "spray_management",
              replacement = "",
              x = x1)
   x1
}

for_rows <- function(head_row, gap = NULL, r_order = NULL, ord_var){
   if(is.null(gap)){gap <- 0}

   stitle_row <- head_row - c(2,
                              15 + gap,
                              32 + (gap*2),
                              59 + (gap*3),
                              99 + (gap*4))

   ord_rows <- order(order(dat1[,ord_var]))

   ks1 <- c(sum(dat1$spray_management == "Early"),
            sum(dat1$spray_management == "Late"),
            sum(dat1$spray_management == "Recommended"),
            sum(dat1$spray_management == "Recommended_plus"),
            sum(dat1$spray_management == "Late_plus"))

   dat2 <- list(stitle_row = stitle_row,

              pred_row = stitle_row - c(15,29,42,19,21),

            trows2 = c((stitle_row[1] - 2.5) - ord_rows[1:ks1[1]],
                       (stitle_row[2] - 2.5) - ord_rows[ks1[1]+1:ks1[2]],
                       (stitle_row[3] - 2.5) - ord_rows[ks1[2]+1:ks1[3]],
                       (stitle_row[4] - 2.5) - ord_rows[ks1[3]+1:ks1[4]],
                       (stitle_row[5] - 2.5) - ord_rows[ks1[4]+1:ks1[5]]
                       ),
            trows3 = ord_rows

              trows = c((stitle_row[1]-1.5):(stitle_row[1]-0.5 - ks1[1]),
                        (stitle_row[2]-1.5):(stitle_row[2]-0.5 - ks1[2]),
                        (stitle_row[3]-1.5):(stitle_row[3]-0.5 - ks1[3]),
                        (stitle_row[4]-1.5):(stitle_row[4]-0.5 - ks1[4]),
                        (stitle_row[5]-1.5):(stitle_row[5]-0.5 - ks1[5])))

   if(is.null(r_order) == FALSE){
      dat2$trows <- dat2$trows[r_order]
   }
   dat2
}

rows1 <- for_rows(156, ord_var = "spray_management")

polys <- data.frame(ref = change_labels(names(coef(PM_mv))),
                    x = coef(PM_mv),
                    ci.lb = PM_mv$ci.lb,
                    ci.ub = PM_mv$ci.ub,
                    rows = rows1$pred_row)

dat1$ID <- 1:116

index1 <- dat1 %>%
   arrange(desc(spray_management), location, desc(grain_MD))%>%
   select(ID) %>%
   mutate(ID2 = order(ID))

forest1  <- metafor::forest(PM_mv, cex = 1.15 , width = 5,
                #order = "fit",
                rows = (index1$ID2)+50,
                ilab = cbind(dat1$trial_ref, dat1$location, dat1$year, 
                             dat1$row_spacing, dat1$host_genotype, dat1$dose,
                             as.character(dat1$spray_management)),
                ilab.xpos = c(-3.3, -2.85,-2.55,-2.35,-2.15,-1.85, -1.5),
                slab = NA, 
                xlim = c(-3.5, 2.5),
                ylim = c(11,157),
                xlab = "Grain yield mean difference",
                addfit = FALSE,
                efac = c(0.5,2,0.2))

@@

### add column headings to the plot
text(c(-3.3, -2.85,-2.55,-2.35,-2.13,-1.85), 156,cex = 1, 
     c("Trial\nReference", "Location", "Year", "Row\nSpacing","Host\nCultivar","DMI dose"),
     font = 2)

text(-0.8, rows1$stitle_row ,cex = 1.3, 
     paste0(polys$ref," Spray Schedule - (tau^2 = " ,round(PM_mv$tau2, digits = 3), ") "),
     font = 2)

text(-3.45, -3:160, cex=1,-3:160)

addpoly(x = polys$x,
        ci.lb = polys$ci.lb,
        ci.ub = polys$ci.ub,
        col ="black",
        rows = polys$rows,
        cex = 1.3,
        efac = 0.2,
        font = "Arial Rounded MT Bold")
abline(h = rows1$pred_row -2)
